---
title: "Calculating Skovoroda and Lankina deviance measure for national elections"
output: html_notebook
---


```{r setup}
library(tidyverse)
library(openxlsx)
library(here)
library(stringi)

election_full <- read.xlsx(here("Data", "Election_data", "precinct_results_2012.xlsx"))

```

```{r}
election_full <- election_full %>%                                        # Create ID by group
  group_by(region) %>%
  dplyr::mutate(temp_id = cur_group_id())

```

Get number of precincts

```{r}
precincts <- election_full %>% group_by(temp_id) %>% summarize(n())
precincts <- precincts %>% rename(n_precincts = `n()`)
```

Get frequency of last-digit zeroes

```{r}
precincts <- precincts %>% add_column(ur_last0_freq = NA)
precincts <- precincts %>% add_column(region = NA)

election_full <- election_full %>% mutate(ur_last = putin %% 10)
#election_full <- election_full %>% mutate(kprf_last = zyuganov %% 10)

for (i in 1:nrow(precincts)){
  election_full_sub <- election_full %>% filter(temp_id == i)
  temp_table_ur <- table(election_full_sub$ur_last)
  precincts$ur_last0_freq[i] <- as.numeric(temp_table_ur[1])
  precincts$region[i] <- unique(election_full_sub$region) %>% stri_trans_general(. , 'cyrillic-latin')
}

```


##Skovoroda and Lankina formula for deviance of last-digit zero

```{r}
precincts$deviance_region <- 2*(precincts$ur_last0_freq*log(precincts$ur_last0_freq/(.1*precincts$n_precincts)) +
                                (precincts$n_precincts - precincts$ur_last0_freq)*log((precincts$n_precincts - precincts$ur_last0_freq)/(.9*precincts$n_precincts)))
```

```{r}
write.csv(precincts, here("Data", "region_deviance_2018.csv"))
```




## Collecting just for the trail region of Dagestan

```{r}
election_dagestan <- election_full %>% filter(region == "Республика Дагестан")

election_dagestan <- election_dagestan %>%                                        # Create ID by group
  group_by(tik) %>%
  dplyr::mutate(temp_id = cur_group_id())

```

Get number of precincts

```{r}
precincts <- election_dagestan %>% group_by(temp_id) %>% summarize(n())
precincts <- precincts %>% rename(n_precincts = `n()`)


```

Get frequency of last-digit zeroes

```{r}
precincts <- precincts %>% add_column(ur_last0_freq = NA)
precincts <- precincts %>% add_column(tik = NA)

election_dagestan <- election_dagestan %>% mutate(ur_last = putin %% 10) #united_russia for parl elections
#election_dagestan <- election_dagestan %>% mutate(kprf_last = kprf %% 10)

for (i in 1:nrow(precincts)){
  election_full_sub <- election_dagestan %>% filter(temp_id == i)
  temp_table_ur <- table(election_full_sub$ur_last)
  precincts$ur_last0_freq[i] <- as.numeric(temp_table_ur[1])
  precincts$tik[i] <- unique(election_full_sub$tik) %>% stri_trans_general(. , 'cyrillic-latin')
}

```

Getting deviance
```{r}
precincts$deviance_tik <- 2*(precincts$ur_last0_freq*log(precincts$ur_last0_freq/(.1*precincts$n_precincts)) +
                                (precincts$n_precincts - precincts$ur_last0_freq)*log((precincts$n_precincts - precincts$ur_last0_freq)/(.9*precincts$n_precincts)))

print(precincts, n = 54)
```


```{r}
write.csv(precincts, here("Data", "dagestan_tik_deviance2012.csv"))
```

20 Kajtagskaâ deviance in 2012: 15.11 (mean 3.31)  19978 voters on the list, 17041 votes for Putin: 85.3%   92.8% relative vote-share for Dagestan as a whole

20 Kajtagskaâ deviance in 2018: 3.47 (mean 1.44)  21298 voters on the list, 18130 votes for Putin 85.12%    90.8% relative for Dagestan as a whole.

While it's not fully convincing--so many years in between--we do see a very large change across the years there.



Next steps: collect deviance for opposition party too? Figure out best way to connect the collected deviances to the main dataset for this. It may be time to just come up with a new master ID list. But this is tricky because of different spellings for some of the regions across years in the big datasets.